The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-10-23 Paper_Analyses.tex
convert to papaja, temporary references fix

---
title             : "The development of infants' responses to mispronunciations - A Meta-Analysis"
shorttitle        : "Mispronunciation Meta-Analysis"

author: 
  - name          : "Katie Von Holzen"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "0221A LeFrak Hall, University of Maryland, College Park, MD 20742"
    email         : "katie.m.vonholzen@gmail.com"
  - name          : "Christina Bergmann"
    affiliation   : "3,4"

affiliation:
  - id            : "1"
    institution   : "Language Development Laboratory, University of Maryland, USA"
  - id            : "2"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "3"
    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
  - id            : "4"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

keywords          : "keywords"
wordcount         : "X"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
citeproc          : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

# bibliography      : ["MISP_MA_BIB.bib"]

# [KATIE] BIBLIOGRAPHY CURRENTLY REMOVED, AS IT IS CAUSING ERRORS WITH PAPAJA
# THIS IS PARTIALLY DUE TO THE WAY I CREATE IT USING MENDELEY. 
# TOO LAZY FOR THE MOMENT TO COMPLETELY OVERHAUL THIS

# BUT, OTHER PROBLEMS INCLUDE HAVING PAPAJA INSTALLED IN THE USER AND NOT SYSTEM LIBRARY
# https://github.com/crsh/papaja/issues/162
# devtools::with_libpaths(new = "/usr/lib/R/library/", install_github('crsh/papaja'))

# AND THE NEED TO SET citeproc: no
# https://github.com/crsh/papaja/issues/96

# STILL NEED TO FIGURE OUT WHAT ACTUAL PROBLEM IS, THIS IS CURRENTLY JUST A WORKAROUND

### Load libraries
library(papaja)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)
library(poibin)
library(tidyverse)

r2 <- function(x){ round(x, 3)}

psig <- function(x){
  ifelse(x < .001, "< .001",
         #ifelse(x < .001, "< .001",
                #ifelse(x < .01, "< .01",
                       ifelse(x > .001 & x < .05, paste("=", r2(x), sep = " "), paste("=", r2(x), sep = " ")))#))
}

# function for creating 1 line paired t.test results
t.xtable <- function(x) as.data.frame(xtable(
  t_out(toutput=x, n.equal = TRUE, welch.df.exact = TRUE, welch.n = NA,
        d.corr = TRUE, print = TRUE)
))

```

```{r ReadIn}

#Get the effect size data
source("scripts/calculateES.R")

```

```{r Preprocess}

db_ET <- db_ET %>%
  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
  filter(mean_age_months < 31)

db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")

# assign language families

db_ET$lang_family = ifelse(db_ET$native_lang=="American English" | db_ET$native_lang=="British English" | db_ET$native_lang=="Dutch" |
db_ET$native_lang=="Danish" | db_ET$native_lang=="Swedish" |
db_ET$native_lang=="English" | db_ET$native_lang=="German", "Germanic", ifelse(db_ET$native_lang == "French" | db_ET$native_lang == "Catalan" | db_ET$native_lang == "Spanish" | db_ET$native_lang == "Catalan-Spanish" | db_ET$native_lang == "Swiss French", 
                                "Romance", "Sino-Tibetian"))

#Split into correct and MP database

db_ET_correct <- db_ET[db_ET$is_correct=="1",]
db_ET_MP <- db_ET[db_ET$is_mp=="1",]

#collapse over nonindependent MP rows for a *general* MP effect

collapse_rows <- function(db){
  db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")

  for(independent in unique(db$collapse)){
    if(length(db[db$collapse==independent])>1){
      sub = db[db$collapse==independent, ]
      sub$d_calc <- median(sub$d_calc)
      sub$d_var_calc <- median(sub$d_var_calc)
      sub$g_calc <- median(sub$g_calc)
      sub$g_var_calc <- median(sub$g_var_calc)
      sub$corr_imputed <- median(sub$corr_imputed)
      db <- db[!(db$collapse==independent),]
      db <- rbind(db, sub[1,])
    }
  }
  return(db)
}

#db_ET_correct = collapse_rows(db_ET_correct)

#db_ET_MP = collapse_rows(db_ET_MP)

#remove outliers, for now we have none, though
db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
                         | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]

db_ET_correct$nooutlier = ifelse(db_ET_correct$g_calc > mean(db_ET_correct$g_calc, na.rm = TRUE) + 3*sd(db_ET_correct$g_calc, na.rm = TRUE) 
                         | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]

# make sure that both correct and mispronounced conditions are considered in descriptives

db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

dat <- bind_rows(db_ET_correct, db_ET_MP)

# need data set of unique short cite by expt_num
# in order to calculate total number of infants

# need data set of unique short cite by condition

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]

```

```{r PlotAPATheme}
# Plotting defaults

#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

# Color Blind palette:
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

```

# Introduction

Acquiring a first language means that young learners are solving a host of tasks in a short amount of time. As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words. Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word. This mispronunciation sensitivity reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes that might signal a change in word meaning. As infants continue to develop into expert language users, their language processing matures and becomes more efficient. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language (e.g. cat-hat). In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover its characteristics and the trajectory of its development.

  At the turn of the millenia, infant language acquisition researchers had established that during their first years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with familiar image pairs, children fixate on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g. baby, dog) and their eye movements to each image were coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. baby). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. vaby). Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than in mispronounced trials, although looks to the target were significantly greater than chance in both types of trials. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological constancy* and *phonological distinctiveness*. Phonological constancy is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between different words that happen to be phonologically similar, such as bad/bed or cat/hat. To successfully recognize words, infants must therefore simultaneously use both phonological constancy and distinctiveness to determine where phonological variation is appropriate and where it changes a word's meaning.

@@

  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability. According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995). This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth. In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and *decrease* as the child matures and learn more words, although children continue to detect mispronunciations.
Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.

  According to a different theoretical framework, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates. PRIMIR (Processing Rich Information from Multidimensional Interactive Representations; Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) describes the development of phonemic categories emerging as the number of word form-meaning linkages increases. Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words. Following this account, we predict an *increase* in mispronunciation sensitivity as infants mature and add more words to their growing lexicon.

@@

  Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task (see Table X), making the current meta-analysis very informative. One study has found evidence for infants to become *less* sensitive to mispronunciations as children develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features). 18-month-olds were sensitive to mispronunciations, regardless of the number of features changed. 24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations. In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.

  In contrast, other studies have found evidence for *greater* mispronunciation sensitivity as children develop. More precisely, the difference in target looking for correct and mispronounced trials is smaller in younger infants and grows as infants develop. Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity. An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (van der Feest & Fikkert, 2015) and 15 to 18 months (Altvater Mackensen et al., 2013) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest and Fikkert (2015) found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning. In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations. These studies award support to the prediction that mispronunciation sensitivity improves with development.

Finally, some studies have found no difference in mispronunciation sensitivity at different ages. Swingley and Aslin (2000) tested infants over a wide age range of 5 months (18 to 23 months).  They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not. This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity. A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey & Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012). These studies award support to the prediction that mispronunciation sensitivity does not change with development.

  Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease? The main hypothesis is related to vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occurring along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months. Knowing more words helps infants shift their focus to the relevant phonetic dimensions needed for word recognition. On the one hand, a smaller lexicon does not require full specification to differentiate between words; as more phonologically similar words are learned, so does the need to have fully detailed representations for those words (Charles-Luce & Luce, 1995). On the other hand, a growing vocabulary is also related to more experience or familiarity with words, which may sharpen the detail of their representation (Barton, 1980).

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008). One notable exception comes from Mani and Plunkett (2010: keps and tups). Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, although receiving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results.

@@

  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955). Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words. By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e. 1-feature, 2-features, 3-features, etc.). The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The development of infants' responses to mispronunciations - A Meta-Analysis},
            pdfauthor={Katie Von Holzen~\& Christina Bergmann},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{The development of infants' responses to mispronunciations - A
Meta-Analysis}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
Bergmann\textsuperscript{3,4}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Language Development Laboratory, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

\authornote{

Correspondence concerning this article should be addressed to Katie Von
Holzen, 0221A LeFrak Hall, University of Maryland, College Park, MD
20742. E-mail:
\href{mailto:katie.m.vonholzen@gmail.com}{\nolinkurl{katie.m.vonholzen@gmail.com}}}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the
field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background},
comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being
addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here
we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals
in direct comparison to what was thought to be the case previously, or
how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general
context}.

Two or three sentences to provide a \textbf{broader perspective},
readily comprehensible to a scientist in any discipline.

}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\section{Introduction}\label{introduction}

Acquiring a first language means that young learners are solving a host
of tasks in a short amount of time. As infants develop into toddlers
during their second and third years they learn new words in earnest
while simultaneously refining their knowledge about the sounds that make
up these words. Before children can correctly pronounce a word, they
already show evidence of sensitivity to slight variations in the
phonological form of that word. This mispronunciation sensitivity
reflects the specificity with which infants represent the phonological
information of familiar words and are sensitive to changes that might
signal a change in word meaning. As infants continue to develop into
expert language users, their language processing matures and becomes
more efficient. In a mature phono-lexical system, word recognition must
balance flexibility to slight variation (e.g., speaker identity,
accented speech) while distinguishing between phonetic details that
differentiate words in their native language (e.g.~cat-hat). In this
paper, we aggregate and analyze the almost 20 years of literature
investigating mispronunciation sensitivity in infants in an attempt to
uncover its characteristics and the trajectory of its development.

At the turn of the millenia, infant language acquisition researchers had
established that during their first years of life, infants are sensitive
to changes in the phonetic detail of newly segmented words (Jusczyk \&
Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
Furthermore, when presented with familiar image pairs, children fixate
on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
\& McRoberts, 1998). Swingley and Aslin (2000) were the first to tie
these lines of research together and investigate mispronunciation
sensitivity in infant familiar word recognition: Children aged 18 to 23
months learning American English were presented with pairs of images
(e.g.~baby, dog) and their eye movements to each image were coded
offline. On \enquote{correct} trials, children heard the correct label
for one of the images (e.g.~baby). On \enquote{mispronounced} trials,
children heard a mispronounced label of one of the images (e.g.~vaby).
Mean proportion of fixation to the target image (here: a baby) was
calculated for both correct and mispronounced trials by dividing the
target looking time by the sum of total looking time to both target and
a distractor (proportion of target looking or PTL). Mean fixations in
correct trials were significantly greater than in mispronounced trials,
although looks to the target were significantly greater than chance in
both types of trials. We refer to this pattern of a difference between
looks to correct and mispronounced words as \emph{mispronunciation
sensitivity} and of looks to the target image above chance as
\emph{recognition}. Swingley and Aslin (2000) concluded that already
before the second birthday, children represent words with sufficient
detail to be sensitive to mispronunciations.

The study of Swingley and Aslin (2000) as well as subsequent studies
examining mispronunciation sensitivity address two complementary
concepts in early phonological development: \emph{phonological
constancy} and \emph{phonological distinctiveness}. Phonological
constancy is the ability to accept phonological variation across
different instances of a word, as long as the variation does not
compromise the overall identity of the word. For example, different
speakers - particularly across genders and accents - produce the same
word with notable acoustic variation, although the word remains the
same. In contrast, phonological distinctiveness describes the ability to
differentiate between different words that happen to be phonologically
similar, such as bad/bed or cat/hat. To successfully recognize words,
infants must therefore simultaneously use both phonological constancy
and distinctiveness to determine where phonological variation is
appropriate and where it changes a word's meaning.

@@

Young infants may begin cautiously in their approach to word
recognition, rejecting any phonological variation in familiar words and
only later learning to accept appropriate variability. According to the
Perceptual Attunement account, this describes a shift away from specific
native phonetic patterns to a more mature understanding of the abstract
phonological structure of words (Best 1994, 1995). This shift is
predicted to coincide with the vocabulary spurt around 18 months, and is
therefore related to vocabulary growth. In this case, we would expect
the size of mispronunciation sensitivity to be larger at younger ages
and \emph{decrease} as the child matures and learn more words, although
children continue to detect mispronunciations. Indeed, young infants are
less likely than older infants to demonstrate recognition of familiar
words (Best, Tyler, Gooding, Orlando, \& Quann, 2009; Mulak, Best, \&
Tyler, 2013) or learn new words (Schmale, Hollich, \& Seidl, 2011) from
accented speakers.

According to a different theoretical framework, young infants may
instead begin with phonologically broad representations for familiar
words and only refine their representations as language experience
accumulates. PRIMIR (Processing Rich Information from Multidimensional
Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin,
2005; Curtin, Byers-Heinlein, \& Werker, 2011) describes the development
of phonemic categories emerging as the number of word form-meaning
linkages increases. Vocabulary growth, therefore, promotes more detailed
phonological representations in familiar words. Following this account,
we predict an \emph{increase} in mispronunciation sensitivity as infants
mature and add more words to their growing lexicon.

@@

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 12 months
(Mani \& Plunkett, 2010), indicating that from early stages of the
developing lexicon onwards, infants can and do detect mispronunciations.
Regarding the change in mispronunciation sensitivity over development,
however, only a handful of studies have compared more than one age group
on the same mispronunciation task (see Table X), making the current
meta-analysis very informative. One study has found evidence for infants
to become \emph{less} sensitive to mispronunciations as children
develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
mispronunciations varying in the number of features changed (see below
for a discussion of the role of features). 18-month-olds were sensitive
to mispronunciations, regardless of the number of features changed.
24-month-olds, in contrast, fixated the target image equally for both
correct and 1-feature mispronounced trials, although they were sensitive
to larger mispronunciations. In other words, for 1-feature
mispronunciations at least, sensitivity decreased from 18 to 24 months,
providing support to the prediction that mispronunciation sensitivity
may decrease with development.

In contrast, other studies have found evidence for \emph{greater}
mispronunciation sensitivity as children develop. More precisely, the
difference in target looking for correct and mispronounced trials is
smaller in younger infants and grows as infants develop. Mani and
Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
English; although all three groups were sensitive to mispronunciations,
15-month-olds showed a less robust sensitivity. An increase in
sensitivity to mispronunciations has also been found from 20 to 24
months (van der Feest \& Fikkert, 2015) and 15 to 18 months (Altvater
Mackensen et al., 2013) in Dutch infants, as well as German infants from
22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest
and Fikkert (2015) found that sensitivity to specific kinds of
mispronunciations develop at different ages depending on language
infants are learning. In other words, the native language constraints
which \emph{kinds} of mispronunciations infants are sensitive to first,
and that as infants develop, they become sensitive to other
mispronunciations. These studies award support to the prediction that
mispronunciation sensitivity improves with development.

Finally, some studies have found no difference in mispronunciation
sensitivity at different ages. Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation effect)
did not. This suggests that as children develop, they are more likely to
look at the target in the presence of a mispronounced label and that age
is not related to mispronunciation sensitivity. A similar response
pattern has been found for British English learning infants aged between
18 and 24 months (Bailey \& Plunkett, 2002) as well as younger
French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, \&
Frauenfelder, 2012). These studies award support to the prediction that
mispronunciation sensitivity does not change with development.

Why would mispronunciation sensitivity change as infants develop, and
would it increase or decrease? The main hypothesis is related to
vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and
PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005; Curtin,
Byers-Heinlein, \& Werker, 2011) accounts situate a change in
mispronunciation sensitivity occurring along with an increase in
vocabulary size, particularly with the vocabulary spurt at about 18
months. Knowing more words helps infants shift their focus to the
relevant phonetic dimensions needed for word recognition. On the one
hand, a smaller lexicon does not require full specification to
differentiate between words; as more phonologically similar words are
learned, so does the need to have fully detailed representations for
those words (Charles-Luce \& Luce, 1995). On the other hand, a growing
vocabulary is also related to more experience or familiarity with words,
which may sharpen the detail of their representation (Barton, 1980).

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
(2010: keps and tups). Here, 12-month-old infants were divided into a
low vocabulary and high vocabulary group based group median vocabulary
size. High vocabulary infants showed greater sensitivity to vowel
mispronunciations than low vocabulary infants, although this was not the
case for consonant mispronunciations. Taken together, although receiving
considerable support from theories of phono-lexical processing in
language acquisition, there is very little evidence for a role of
vocabulary size in mispronunciation sensitivity. In our current
meta-analysis, we include the relationship between mispronunciation
sensitivity and vocabulary size to further disentangle the disconnect
between theory and experimental results.

@@

In designing their mispronunciation stimuli, Swingley and Aslin (2000)
chose consonant mispronunciations that were likely to confuse adults
(Miller \& Nicely, 1955). Subsequent research has settled on
systematically modulating phonemic features to achieve mispronunciations
of familiar words. By utilizing mispronunciations consisting of phonemic
changes, these experiments examine infants' sensitivity to factors that
change the identity of a word on a measurable level (i.e.~1-feature,
2-features, 3-features, etc.). The importance of controlling for the
degree of phonological mismatch, as measured by number of features
changed, is further highlighted by studies that find graded sensitivity
to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
2011) feature changes.

Although most research examining sensitivity to mispronunciations
follows a similar design, there are some notable differences. For
example, Swingley and Aslin (2000) presented infants with pairs of
familiar images, one serving as the labeled target and one as the
unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
infants with pairs of familiar (labeled target) and unfamiliar
(unlabeled distractor) objects. By using an unfamiliar object as a
distractor, the infant is presented with a viable option onto which the
mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
Hansen, 2003). Infants ages 24 and 30 months associate a novel label
with an unfamiliar object, although only 30-month-olds retained this
label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
18-month-olds did not learn to associate a novel label with an
unfamiliar object, providing evidence that this ability is developing
from 18 to 30 months. We may find that if mispronunciation sensitivity
changes as children develop, that this change is modulated by whether
the distractor used is familiar or unfamiliar. Although mispronunciation
sensitivity in the presence of a familiar compared to unfamiliar
distractor has not been directly compared, the baseline preference for
familiar compared to novel stimuli is also thought to change as infants
develop (Hunter \& Ames, 1988). Furthermore, young children have been
found to look longer at objects for which they know the name, compared
to objects of an unknown name (Schafer \& Plukett, 1998). In other
words, in absentia of a label, infants may be more or less likely to
fixate on an unfamiliar object. To account for inherent preferences to
the target or distractor image, mispronunciation experiments typically
compare the increase in fixations to the target image from a silent
baseline to post-labeling or present the same yoked pairs of target and
distractor images in in both a correct and mispronounced labelling
context. Considering this evidence, we may expect that in older, but not
younger, children, the presence of an unfamiliar distractor may lead to
greater mispronunciation sensitivity than in the presence of a familiar
distractor.
